\documentclass[11pt]{resume} %the resume.cls file has to be in the same folder as this file

%%  Math 201 Spring 2019
%%  Daniel Alvarez
%%% Resume

\usepackage[paper=letterpaper,total={6.5in,9.2in},top=0.8in, left=1in]{geometry}


\usepackage{xspace}
\newcommand{\latex}{\LaTeX\xspace}
\newcommand{\bold}[1]{\textbf{#1}}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{verbatim}

\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,      
	urlcolor=cyan,
}


\newcommand{\tname}[1]{\Large\textbf{#1}}

\name{Daniel Alvarez} 
\address{Whatsapp: +1 (868)377-6679}
\address{daniel.l.alvarez@gmail.com}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
\begin{document}
	
\begin{rSection}{Objective}
	To acquire skills congruent with my field of study and to make tangible contributions to the company for which I work.
\end{rSection}
\begin{rSection}{Work Experience}
\begin{itemize}
	
	\item\bold{IT Help Desk / Mercyhurst University} \quad August 2020 - Present (Grad Employee - Remote)\\
	I am responsible for remotely troubleshooting issues for students and faculty. My duties include managing an Azure directory of users, registering user devices on the network and ensuring user account are kept secure.
	\\
	
	\item\bold{Web Developer/ Perenco Oil \& Gas} \quad June 2019 – August 2019 (Internship)\\
	I was responsible for designing and developing a web site for the Operations department to be used within the company's internal network.\\
	
	\item\bold{Technical Support / Mercyhurst Campus Ministry} \quad November 2018 - December 2019
	 I was responsible for designing the Campus Ministry web page  \url{https://lakersmercyhurst.sharepoint.com/sites/SPO_STU_CampusMinistry}.\\
	I was also responsible for completing the various tasks necessary for the execution of events put on by Campus Ministry.\\
	
	\item\bold{IT Technician/ DirecOne} \quad May 2017 – August 2017 (Internship)\\
	I was responsible for maintaining the optimal functioning of the company’s software and hardware systems and equipment. My duties included testing and troubleshooting, setting up of workstations and other communication technology and equipment.\\
	
	\item\bold{Student Tutor/Mercyhurst University} \quad November 2016 - December 2019\\
	Provided individualized and group assistance to students in the following courses:\\ Data Science, Financial Accounting, Macroeconomics, Microeconomics, Business Stats, Computer Science, Linear \& Non-Linear Data Structures and Algorithms.\\
	Guided students with the design and construction of programming projects.
	\\
	
\end{itemize}
\end{rSection}

\begin{rSection}{Education}

\begin{itemize}
	\item\bold{Mercyhurst University}\\
	Masters of Science Data Science  (Estimated graduation May 2022).
	
	\item\bold{Mercyhurst University}\\
	Bachelor of Arts Information Technology and Mathematical Economics (December 2019).

\end{itemize}
\end{rSection}
\vspace{1in}
\begin{rSection}{Tech Languages/Skills}
\begin{itemize}
\item Online Portfolio: \url{https://danny-alvarez.github.io/portfolio/index.html}
\item Back-end Technologies: C\#, PHP, MySQL
\item Front-end Technologies: HTML5, CSS3, JavaScript, jQuery, Microsoft Share Point
\item Frameworks and Libraries: .NET Framework (Windows forms, Web Forms), Entity Framw
\item Type Setting Technology: \LaTeX\xspace (This resume was made using \LaTeX)
\item Operating systems: Windows, Linux (Ubuntu)
\item Other Languages:Python, SQL, bash, PHP
\item Window's Suite: Word, Excel, Access, PowerPoint
\item Game Engines: Unity
\end{itemize}
\end{rSection}


\begin{rSection}{Volunteer/Other Experience}
	\begin{itemize}
		\item\bold{Athletics}
		I am an athlete in the sport of Water Polo. I played on varsity team at Mercyhurst for all four years and have represented Trinidad and Tobago at CARIFTA, CCCAN (Central American and Caribbean Swimming Federation), Pan Am and CAC Games tournaments from age 15 to the present. I was also a National Youth Teams assistant coach during 2014-2015. 
		\item\bold{Carpe Diem}\\
		I was as a nominated leader for a three day retreat event done every semester for students by students of Mercyhurst. My specific role involved maintaining a database of applicants and coordinating group activities on the day of the retreat. 
	\end{itemize}
\end{rSection}


\end{document}